{\includegraphics[width=3cm, height=2.5cm]{Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TB.jpg} \\ {Technical Documentation for TersectBrowser+}

### 2025-05-05 TechDoc/TechDoc.tex
Edits to tech doc

\begin{itemize}
    \item open a genome browser within Tersect Browser and investigate specific variants.
    \item see specific genes of interests against suspected introgressions. 
    \item identify areas where high-impact variants are visible. 
    \item be able to genereate DNA barcodes for the varioius cultivars and species in the dataset. 
    \item to be able to load additional datasets, including for other crops. 
\end{itemize}

@@

The Admin is defined as an individual with bioinformatics and software design knowledge, background comprehension for all sections of this Technical Documentation, and acting to facilitate the use of a deployed TersectBrowser+ by the plant breeder main user of the software. When a new dataset is requested for deployment on TersectBrowser+, the Admin will need to follow the below steps:
\begin{enumerate}
    \item Collect background context and required data from the user.
\begin{itemize}
    \item Reference genome in fasta format (may be compressed). Size and chromosome number will impact the speed of dataset upload and deployment - TersectBrowser+ has been tested with a genome size of ~1GB, and 20 chromosome pairs.
    \item Resequenced genome dataset in VCF format (may be compressed, as a multi-sample VCF or as a directory of individual files). TersectBrowser+ has been tested with a dataset size of ~500 VCF files representing individual accessions. 
    \item Any metadata associated with different accessions in the dataset, such as wild variety vs domesticated variety. \hl{This should be provided in a text file.}
    \item A GFF file of gene model information for the reference genome, produced using SNPeff software. If not using SNPeff, ensure that variant impact levels are categorised into `High', `Medium', and `Low' impact. If not provided, the gene model track in the Variant Browser will be unavailable. 
    \item Whether there are prior identified introgressions known to be functionally relevant for the species. These can be used to `check' the ability of TersectBrowser+ to identify introgressed regions for the specified dataset.
\end{itemize}
    \item Clone the GitHub repository of TersectBrowser+ to the local machine. Follow the README from \hyperlink {https://github.com/Tersect-Browser/Tersect-browser.git}{TersectBrowser+ GitHub} for installation instructions.
    \item Download relevant files from section (1) to a new folder within the root directory of the local Tersect-browser repository.
    \item Set environment variables \verb+fasta+, \verb+gff+, and \verb+vcfs+ according to their new location relative to the root of Tersect-browser.
    \item Run the script \verb+setup_new_tbrowser_dataset.py+ using the environment variables of files as input:

@@

Finally, callHighlightBins() is called, which itself calls highlightBins() from the bin-draw.service, passing as arguments the current interval start position, binsize, displayed accessions in an ordered format, and the searched accessions.  
\paragraph{\hl{Clear Button }}
The clear button is located to the right of the \verb+Open variant search+ button and styled with \verb+fa fa-refresh+. It contains the event handler \verb+(click)="refreshBin()"+ that calls the \verb+refreshBin()+ method in \verb+BinDrawService+.
This method calls \verb+generatePlotArray()+, which re-creates the bin view, and \verb+updateCanvas()+, which redraws the canvas using the re-created bin view.

>>>>

\begin{itemize}
    \item open a genome browser within Tersect Browser and investigate specific variants.
    \item visualise gene models in areas of suspected introgressions.
    \item identify areas where high-impact variants are visible. 
    \item be able to genereate DNA barcodes for the varioius cultivars and species in the dataset. 
    \item to be able to load additional datasets, including for other crops. 
\end{itemize}

@@

The Admin is defined as an individual with bioinformatics and software design knowledge, background comprehension for all sections of this Technical Documentation, and acting to facilitate the use of a deployed TersectBrowser+ by the plant breeder main user of the software. When a new dataset is requested for deployment on TersectBrowser+, the Admin will need to follow the below steps:
\begin{enumerate}
    \item Collect background context and required data from the user.
\begin{itemize}
    \item Reference genome in fasta format (may be compressed). Size and chromosome number will impact the speed of dataset upload and deployment - TersectBrowser+ has been tested with a genome size of ~1GB, and 20 chromosome pairs.
    \item Resequenced genome dataset in VCF format (may be compressed, as a multi-sample VCF or as a directory of individual files). TersectBrowser+ has been tested with a dataset size of ~500 VCF files representing individual accessions. VCF files should be produced using SNPeff software. If not using SNPeff, ensure that variant impact levels are categorised into `High', `Moderate', and `Low' impact. If not provided, the gene model track in the Variant Browser will be unavailable. 
    \item Any metadata associated with different accessions in the dataset, such as wild variety vs domesticated variety. \hl{This should be provided in a text file.}
    \item A GFF file of gene model information for the reference genome. 
    \item Whether there are prior identified introgressions known to be functionally relevant for the species. These can be used to `check' the ability of TersectBrowser+ to identify introgressed regions for the specified dataset.
\end{itemize}
    \item Clone the GitHub repository of TersectBrowser+ to the local machine. Follow the README from \hyperlink {https://github.com/Tersect-Browser/Tersect-browser.git}{TersectBrowser+ GitHub} for installation instructions.
    \item Download relevant files from section (1) to a new folder within the root directory of the local Tersect-browser repository.
    \item Set environment variables \verb+fasta+, \verb+gff+, and \verb+vcfs+ according to their new location relative to the root of Tersect-browser.
    \item Run the script \verb+setup_new_tbrowser_dataset.py+ using the environment variables of files as input:

@@

Finally, callHighlightBins() is called, which itself calls highlightBins() from the bin-draw.service, passing as arguments the current interval start position, binsize, displayed accessions in an ordered format, and the searched accessions.

\paragraph{\hl{Clear Button }}
The clear button is located to the right of the \verb+Open variant search+ button and styled with \verb+fa fa-refresh+. It contains the event handler \verb+(click)="refreshBin()"+ that calls the \verb+refreshBin()+ method in \verb+BinDrawService+.
This method calls \verb+generatePlotArray()+, which re-creates the bin view, and \verb+updateCanvas()+, which redraws the canvas using the re-created bin view.
